\abstract{\addtocontents{toc}{\vspace{1em}} 
	
	The use of internet has had many positive effects on education. It has provided us with the means to educate each and everyone without any discrimination, and any limitations (term relative only in terms of education, not the accessibilty limitation). I t overcomes both the limitations that students mostly have, which is time and the amount of space required for various books. This also benefits the teachers who have vast access to all the information and resources from the internet.
	\\
	2020 was the year that challenged all the education systems to re-think the way students could be educated and also resulted in many educational conferences being cancelled. But this also led us to switching to new ideas/processes using internet as the backbone of all the work we do. My project also involved converting an offline exhibition that was held every year to an online variant. 
	\\
	This exhibition has been converted to an online variant wherein scientists, researchers, and scholars from various universities come in and explain about their research and the impact that it produces in real-world. The design and development of the website took nearly 7 months comprising various applications, technolgies, illustrators, animators...etc. For the wireframing and the prototype of the website Adobe XD was the most used application other than Figma and Framer X. The front-end of the website was build using ReactJs framework, using Tailwind-Css, Twin Macro and Styled-Components to style the website. The data is being populated using Google Sheets API as they wanted to quickly keep changing content and wanted that to be reflected in the website without the hassle of updating it constantly to a database like postgres or Mongo as that would also introduce a curve to learn for the non-technical people who were managing the exhibition. The website was put into production using Nginx using the on-site servers. 
	
	}

\textbf{\textit{Keywords}:} React.js, Tailwind, Nginx, Google Sheet API, Git

\clearpage % Start a new page